---
title: "Untitled"
author: "Yihan Feng"
date: "11/16/2020"
output: github_document
---


```{r setup, include = FALSE}
library(tidyverse)
library(rvest)
library(dplyr)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Read in the data.

```{r}
homicide_df = 
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


Let's look at this a bit

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate ........

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```



```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```



## Problem 2 

### import, unnest, and clean the data sets

```{r, message=FALSE}
path_df <- 
  tibble(
    path = list.files("./lda_data")
    ) %>% 
  mutate(
    path = str_c("./lda_data/", path),
    data = map(.x = path, ~read_csv(.x))) %>%
  unnest() %>%
  mutate(
    path = str_replace(path, "./lda_data/", ""), 
    path = str_replace(path, ".csv", "")
  ) %>%
  separate(path, into = c("group", "id"), sep = "_") %>%
  pivot_longer(
    week_1 : week_8, 
    names_to = "week", 
    names_prefix = "week_",
    values_to = "observation"
  ) %>%
  mutate(
    group = str_replace(group, "con", "control"),
    group = str_replace(group, "exp", "experiment")
  )
```


### Spaghetti plot

```{r}
path_plot <- path_df %>%
  ggplot(aes(x = week, y = observation, group = id, color = id)) + 
  geom_line(alpha = 0.8) + 
  facet_grid(~group) +
  labs(title = "Observations on Each Subject Over Time")
path_plot
```

According to the Spaghetti plot, the experimental group shows increasing values of observation in eight weeks. Comparatively, the control group doesn't have obvious increasing or decreasing in observation values overall. For both groups, the observation values are not increasing gradually or keeping constant over time, but fluctuating a lot. 



## Problem 3

### Simulation

In this simulation, we want to explore power in a one-sample t-test.
/
Null hypothesis: $\mu$ equals 0
/
Alternative hypothesis: $\mu$ doesn't equal 0
/

Set up the simulation function and t test

```{r}
set.seed(2333)

sim_fxn <- function(n = 30, mu, sigma = 5){
  x = rnorm(n, mean = mu, sd = sigma)
  test <- t.test(x = x, alternative = "two.sided", conf.level = 0.95) %>%
    broom::tidy() %>%
    select(estimate, p.value)
}
```


simulation when mu equals 0
```{r}
sim_mu_0 <- rerun(5000, sim_fxn(mu = 0)) %>%
  bind_rows()
```


simulation when mu equals 0, 1, 2, 3, 4, 5, 6
```{r}
sim <- 
  tibble(mu = c(0,1,2,3,4,5,6)) %>%
  mutate(output = map(.x = mu, ~rerun(5000, sim_fxn(mu = .x))),
         result = map(output, bind_rows)) %>%
  select(-output) %>%
  unnest()  
```


### Plots

Plot 1: power of the test (y) vs. the true value of mu (x)

```{r message = FALSE}
sim_plot_1 <- 
  sim %>%
  group_by(mu) %>%
  summarize(p_value = sum(p.value < 0.05), 
            number = n(), 
            reject_prop = p_value/number) %>%
  ggplot(aes(x = mu, y = reject_prop)) + 
  geom_point() + 
  labs(
    x = "True Mean", 
    y = "Proportion of Rejecting Null Hypothesis"
  )

sim_plot_1
```

According to Plot 1, as the true mean increases, the proportion of rejecting null hypothesis also increases. In other words, as the effect size increases, the power of the test also increases. 



Plot 2: the average estimate of $\hat{\mu}$ (y) vs. true value of $\mu$ (x)

```{r message = FALSE}
sim_plot_2 <- 
  sim %>%
  group_by(mu) %>%
  summarize(estimate_avg = mean(estimate)) %>%
  ggplot(aes(x = mu, y = estimate_avg)) + 
  geom_point() +
  geom_smooth(color = "green") +
  labs(
    x = "True Mean", 
    y = "Average of Estimated Mean", 
    title = " Average of Estimated Mean vs. True Mean Among All Samples"
  )

sim_plot_2
```




Plot 3: the average estimate of $\hat{\mu}$ in rejected null hypothesis (y) vs. true value of $\mu$ (x)


```{r message = FALSE}
sim_plot_3 <- 
  sim %>%
  filter(p.value < 0.05) %>%
  group_by(mu) %>%
  summarize(estimate_avg = mean(estimate)) %>%
  ggplot(aes(x = mu, y = estimate_avg)) + 
  geom_point() +
  geom_smooth(color = "blue") +
  labs(
    x = "True Mean", 
    y = "Average of Estimated Mean",
    title = " Average of Estimated Mean vs. True Mean Among Rejected Samples"
  )

sim_plot_3
```

According to Plot 2 and Plot 3, 